Are populations like a circuit? The relationship between isolation by distance and isolation by resistance

### 2018-10-19 isolation_by_coalescence.tex
added note abt mcrae
fixed typos, added figure

Although commute times are uniquely determined by movement rates, the reverse is not true.
Commute times only depend on the symmetric part of $H$ --
given an skew-symmetric matrix $Z$ (so that $Z + Z^T = 0$),
any Markov chain that has hitting times given by $H_\epsilon = H + \epsilon Z$ for some $\epsilon$
will have the same commute times.
The resulting hitting times may not be valid --
if we let $G_\epsilon$ be the matrix constructed by applying equation \eqref{eqn:G_from_H} to $H_\epsilon$,
% (assuming this is invertible),
then it is not guaranteed that the offdiagonal elements of $G_\epsilon$ are all nonnegative, as required.
(It is always true that rows of $G_\epsilon$ sum to zero.)
We provide a small concrete example in Appendix \ref{ss:simple_example}.
However, since $G$ and $H$ are continuous functions of each other,
if all offdiagonal elements of $G$ are strictly positive,
then there exists a positive $\epsilon_0$ such that all $G_\epsilon$ for $\epsilon < \epsilon_0$
do define valid Markov chains, all with the same commute times.

@@

Thanks to David Levin for useful suggestions regarding hitting time calculations,
to Paul Marjoram for useful comments,
and to Brad Shaffer and Evan McCartney-Melstad for useful discussions
and providing the genetic distance data for desert tortoises.
\plr{ERIK: also John, Hossein, Desi, ???}

@@

\begin{figure}
\centering
\includegraphics[scale=.6]{figs/mult_noise}
\caption{Boxplots of the mean absolute error
defined to be the absolute value difference between the true value and posterior median,
averaged across movement parameters $g$ for each of the 25 graphs in each situation.
Each box is labeled with the relative amount of noise added to $H$ to make $\hat{H}$.
The top left shows the results for symmetric graphs 
when there is a single coalescence parameter for all locations,
the top right for symmetric graphs 
when there is a separate coalescence parameter for each location,
the bottom left for asymmetric graphs 
when there is a single coalescence parameter for all locations,
and the bottom right for asymmetric graphs 
when there is a separate coalescence parameter for each location.}
\label{fig:mult_noise}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=.6]{figs/mult_noise_iqr}
\caption{Boxplots of the mean interquartile ranges of the posterior distributions of $g$
for each of the 25 graphs in each situation.
Each box is labeled with the relative amount of noise added to $H$ to make $\hat{H}$.
Subplot locations for each situation are the same as in Figure \ref{fig:mult_noise}.
%The top left shows the results for symmetric graphs 
%when there is a single coalescence parameter for all locations,
%the top right for symmetric graphs 
%when there is a separate coalescence parameter for each location,
%the bottom left for asymmetric graphs 
%when there is a single coalescence parameter for all locations,
%and the bottom right for asymmetric graphs 
%when there is a separate coalescence parameter for each location.
}
\label{fig:mult_noise_iqr}
\end{figure}

>>>>

Although commute times are uniquely determined by movement rates, the reverse is not true.
Commute times only depend on the symmetric part of $H$ --
given a skew-symmetric matrix $Z$ (so that $Z + Z^T = 0$),
any Markov chain that has hitting times given by $H_\epsilon = H + \epsilon Z$ for some $\epsilon$
will have the same commute times.
The resulting hitting times may not be valid --
if we let $G_\epsilon$ be the matrix constructed by applying equation \eqref{eqn:G_from_H} to $H_\epsilon$,
% (assuming this is invertible),
then it is not guaranteed that the offdiagonal elements of $G_\epsilon$ are all nonnegative, as required.
(It is always true that rows of $G_\epsilon$ sum to zero.)
We provide a small concrete example in Appendix \ref{ss:simple_example}.
However, since $G$ and $H$ are continuous functions of each other,
if all offdiagonal elements of $G$ are strictly positive,
then there exists a positive $\epsilon_0$ such that all $G_\epsilon$ for $\epsilon < \epsilon_0$
do define valid Markov chains, all with the same commute times.

@@

Thanks to David Levin for useful suggestions regarding hitting time calculations,
to Paul Marjoram for useful comments,
and to Brad Shaffer and Evan McCartney-Melstad for useful discussions
and providing the genetic distance data for desert tortoises.
We would also like to gratefully acknowledge the immense positive impact that Brad McRae \citep[1966--2017;][]{lawler2018tribute}
has had on landscape genetics and conservation biology through the introduction of landscape resistance.
We hope this paper helps to carry forward this work.
\plr{ERIK: also John, Hossein, Desi, ???}

@@

\begin{figure}
\centering
\includegraphics[scale=.6]{figs/mult_noise}
\caption{Boxplots of the mean absolute error
defined to be the absolute value difference between the true value and posterior median,
averaged across movement parameters $g$ for each of the 25 graphs in each situation.
Each box is labeled with the relative amount of noise added to $C$ to produce the values used for inference.
The top left shows the results for symmetric graphs 
when there is a single coalescence parameter for all locations,
the top right for symmetric graphs 
when there is a separate coalescence parameter for each location,
the bottom left for asymmetric graphs 
when there is a single coalescence parameter for all locations,
and the bottom right for asymmetric graphs 
when there is a separate coalescence parameter for each location.}
\label{fig:mult_noise}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=.6]{figs/mult_noise_iqr}
\caption{Boxplots of the mean interquartile ranges of the posterior distributions of $g$
for each of the 25 graphs in each situation.
Each box is labeled with the relative amount of noise added to $C$ to produce the values used for inference.
Subplot locations for each situation are the same as in Figure \ref{fig:mult_noise}.
%The top left shows the results for symmetric graphs 
%when there is a single coalescence parameter for all locations,
%the top right for symmetric graphs 
%when there is a separate coalescence parameter for each location,
%the bottom left for asymmetric graphs 
%when there is a single coalescence parameter for all locations,
%and the bottom right for asymmetric graphs 
%when there is a separate coalescence parameter for each location.
}
\label{fig:mult_noise_iqr}
\end{figure}
